DeloreanJS: Un Debugger en el Tiempo para JavaScript

### 2019-04-13 paper/main.tex
final

>>>>

Aunque las herramientas de {\em Runtime Verifications} no son necesariamente debuggers, ellas tienen un comportamiento a \deloreanjs porque permiten encontrar errores durante la ejecuci\'on de una aplicaci\'on. Entre las herramientas disponibles, podemos encontrar PQL~\cite{martinAl:oopsla2005}, PTQL~\cite{goldsmithAl:oopsla2005} y JavaMOP~\cite{meredithAl:jsttt2011,chen:oopsla2007}

%PQL. Program Query Language (PQL) [6] is a tool to detect errors and check- /force protocols of programming (e.g., file handling). This tool uses a static analyzer to reduce the possible matches and then uses a dynamic matcher that really matches a given pattern. A developer expresses a pattern using an AST description (using a Java-like syntax). The matching process (i.e., dynamic matcher) uses a specialized state machine. The advice can only use the execute, which is used to execute a method before the last join point matched, or replace, used to replace the original computation of the last matched join point.
%PTQL. Program Trace Query Language (PTQL) [12] is another tool to detect errors. Developers use the SQL language to express a pattern, which is actually a SQL query. Join points are stored in databases, which are used by its matching process, named PARTIQLE, to match a query. PTQL does not allow developers to take actions if a pattern is matched, i.e., there is no advising process in PTQL.
%JavaMop. JavaMop [15, 27, 28] is a generic and efficient runtime-verification framework for Java. Patterns in JavaMop can be expressed in different (pre- viously defined) domain-specific languages: regular expressions, context-free grammars, linear temporal logic, string rewriting system [29], etc. This last pattern language is Turing complete. However, the JavaMop patterns are not first-class values, reusable, and composable. A fixed set of matching process semantics is available for the developers. As JavaMop compiles their code to AspectJ code, the JavaMop advising process follows the same guidelines of AspectJ for this process.
